Carbonate chemistry at Ny-Ålesund

### 2022-08-26 awipev-CO2.Rmd
refined figs for paper

air_sea_month <- d_all %>%
  dplyr::select(monthd, f_air_sea) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_month <- ggplot(data = air_sea_month) +
  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
  lims(y = c(-30, 0)) +
  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
#p_f_air_sea_month
ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")

p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_month
ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
knitr::include_graphics("figures/air-sea_CO2_flux.png")
#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
```

>>>>

air_sea_month <- d_all %>%
  dplyr::select(monthd, f_air_sea) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_month <- ggplot(data = air_sea_month) +
  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
  lims(y = c(-30, 0)) +
  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")

p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_month
ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
knitr::include_graphics("figures/air-sea_CO2_flux.png")

# For paper
size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 12 # font size labels
# temp_insitu_11m
ts_air_sea <- air_sea_month %>%
  ggplot(aes(x = montht, y = f_air_sea), na.rm = TRUE) +
  geom_col(colour="blue", fill = "blue",  alpha = alpha, stat="identity") +
  lims(y = c(-30, 0)) +
  geom_hline(yintercept = 0)+
  labs(title="",x="Month", y=latex2exp::TeX("Air-sea CO$_2$ flux (mmol $m^{-2}$ month$^{-1}$)")) +
  Mytheme(size_labs = size_labs)
ts_air_sea
ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")

#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
```
